Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-09 text/src/article.tex
Delete tables section
Add text for figure 1

  \subsection*{Figure 1 - Sample figure title}

  A short description of the figure content should go here.

\section*{Tables} %{{{1

  \subsection*{Table 1 - Sample table title}
    Here is an example of a \emph{small} table in \LaTeX\ using  
    \verb|\tabular{...}|. This is where the description of the table 
    should go. \par \mbox{}
    \par
    \mbox{
      \begin{tabular}{|c|c|c|}
        \hline \multicolumn{3}{|c|}{My Table}\\ \hline
        A1 & B2  & C3 \\ \hline
        A2 & ... & .. \\ \hline
        A3 & ..  & .  \\ \hline
      \end{tabular}
      }
  \subsection*{Table 2 - Sample table title}
    Large tables are attached as separate files but should
    still be described here.

>>>>

\subsection*{Figure 1 - Example of scaffolder file}

An example scaffold file written using the YAML syntax \cite{yaml}. The
scaffold file contains three entries. Each entry is delimited by a `-' on a new
line. The first entry is an example adding a simple sequence. The second entry
inserts an unresolved gap region into the scaffold. The final entry illustrates
a more complex examplea where the sequece is trimmed, reversed and has
additional sequence inserted \pb
